---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 5, 
  fig.height = 3,
  fig.align='center',
  fig.path = "man/figures/README-"
)
```

# fRegression

[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/paulnorthrop/fRegression?branch=main&svg=true)](https://ci.appveyor.com/project/paulnorthrop/fRegression)
[![R-CMD-check](https://github.com/paulnorthrop/fRegression/workflows/R-CMD-check/badge.svg)](https://github.com/paulnorthrop/fRegression/actions)
[![Coverage Status](https://codecov.io/github/paulnorthrop/fRegression/coverage.svg?branch=main)](https://codecov.io/github/paulnorthrop/fRegression?branch=main)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/fRegression)](https://cran.r-project.org/package=fRegression)
[![Downloads (monthly)](https://cranlogs.r-pkg.org/badges/fRegression?color=brightgreen)](https://cran.r-project.org/package=fRegression)
[![Downloads (total)](https://cranlogs.r-pkg.org/badges/grand-total/fRegression?color=brightgreen)](https://cran.r-project.org/package=fRegression)

## Rmetrics - Modelling Extreme Events in Finance

The **fRegression** package is a collection of functions for linear and non-linear regression modelling. It implements a wrapper for several regression models available in the base and contributed packages of R.

### An example

The following code simulates some regression data and fits various models to these data.

```{r, echo = FALSE}
set.seed(6082022)
```

```{r}
library(fRegression)
# Simulate data: the response is linearly related to 3 explanatory variables 
x <- regSim(model = "LM3", n = 100)
  
# Linear modelling       
regFit(Y ~ X1 + X2 + X3, data = x, use = "lm") 

# Robust linear modelling    
regFit(Y ~ X1 + X2 + X3, data = x, use = "rlm") 

# Generalised additive modelling       
regFit(Y ~ X1 + X2 + X3, data = x, use = "gam")  

# Projection pursuit modelling
regFit(Y ~ X1 + X2 + X3, data = x, use = "ppr") 

# Feed-forward neural network modelling   
regFit(Y ~ X1 + X2 + X3, data = x, use = "nnet") 

# Polychotonous Multivariate Adaptive Regression Splines
regFit(Y ~ X1 + X2 + X3, data = x, use = "polymars")
```

### Installation

To get the current released version from CRAN:

```{r installation, eval = FALSE}
install.packages("fRegression")
```
